\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
Updated section 4.2

\item Areas of Interest (AOI):   
\item Heat-maps:

@@

>>>>

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the model, the object and the caption. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{nokia.jpg}
    \caption{Example of dividing a screen in Areas of interest.
    source: http://eyetracking.com.ua/eng/visualization/12.html}
    \label{aoi}
\end{figure}

\item Heat-maps:

@@

Dual eye-tracking is more complicated to analyse than the solo eye-tracking, for the sole reason of the social dimension being involved in the users' behaviour. Following are the two main points to keep in mind while analysing the social behaviour of a collaborating pair of users:
